\section{Evil scientist game with difficult name we could not remember}

The world generation algorithm used in this game is well know to make for realistic natural environments. I was also pleased to hear that the algorithm was implemented such that a single seed generates consistent map blocks. This enables the blocks to be loaded dynamicaly since no other data than the inital seed is needed to generate them. In our game we wanted a urban environment, but if we wanted a more natural environment, this algorithms would be very useful.

Given such a good algorthim to generate a realistic environment I was slightly disappointed in the cramped view on it. I would have liked to zoom out and see more of it at once.

%Although the appeal of the game is very important, the generated environment did not really play a role in the gameplay. I would be very impressed if elements in the environment

The three AIs in the game (rabbit, platipus duck, unicorn) shows signs of learning, and effectively made it hard to achieve your goals. The zombie compangon showed even clearer signs of learning, but as they explained, these learning steps were hardcoded ``level ups'' of the zombie. Nevertheless, the zombie showed some nice skills in helping the evil scientist.

When we started development of our game, we had something similar in mind with our zombie AI as they did with their rabbit, platipus duck and unicorn AIs. Luckily we very quickly found out that we did not have the time for that. As the devlopers of the evil scientist game said, they spend about half of their time on the AI, something we were unable to do.

The gameplay itself felt good and stable. The main disappointment was the lack of feedback on hits. We could see attack animations of all creatures, but the user had to derive from the decrement in health that the attacks were successful. Simply showing a the damage as a number on the character that was hit would have given the user a much better feeling about what was happening.

This brings me to the sounds. I heard sounds that seemed to bo accomanied with hits, though, these were not played with every hit. Some extra short sounds could really have contributed to the feel of the game. Apart from that, the sounds were very well done.

Overall I am very impressed by the game. Great graphics, working AI and stable gameplay.