\chapter{Summary}

Our assignment is to create a game incorporating both Artificial Intelligence and Computer Graphics and showcasing these components. The general concensus was that Artificial Intelligence would have to be more influential in devising our game concept since it will affect gameplay more. To showcase the Artificial Intelligence component we wanted the concept to include varying levels of intelligence. Showcasing the Computer Graphics component would be easyer as a modern computer game of any genre is inherently graphical.

\section{Conception}

After considering various genres of videogames we decided on strategy as the preferred genre for our game. This would allow for interesting Artificial Intelligence implementations and seemed generally fun. To include the varying levels of intelligence, enemy variety came to mind. The past few years there has been a trend in videogames producing a meriad of different zombie themed games which featured significant enemy variety. Our concept will combine  post-apocalyptic zombie game  elements with the real time strategy genre.

\section{Crouching Zombie Hidden Viking}

During the conceptualisation phase we came up with the slightly humorous "Crouching Zombie Hidden Viking" as a name for our game. The player will control a group of organized post-apocalyptic survivors calling themselves vikings in an attempt to rid the world of the numerous zombies. The vikings will have to gain strength though by gathering resources, men and by staying alive in the process.

